---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

The `commarobust` pacakge does two things: 

1. With the `commarobust()` function, you can easily estimate robust standard errors on your model objects. Almost as easy as Stata!

2. You can easily prepare your standard errors for inclusion in a stargazer table with `makerobustseslist()`. I'm open to better names for this function.

Install from Github!

```{r,eval=FALSE}
install.packages("devtools")
devtools::install_github("acoppock/commarobust")
```

Check it out:

```{r}
library(commarobust)
library(randomizr) # For easy random assignments
Z <- complete_ra(100)
Y <- 5 + 10*Z + rnorm(100)
fit <- lm(Y ~ Z)
commarobust(fit)
```

And now in Stargazer. See how the intercept doesn't have stars even though the control group mean is statistically significantly larger than zero? Nice!

```{r, message=FALSE, results='asis'}
library(stargazer)
Z_1 <- complete_ra(100)
Y_1 <- 10 + 5*Z_1 + rnorm(100)
Z_2 <- complete_ra(100)
Y_2 <- 10 + 2*Z_2 + rnorm(100)

fit_1 <- lm(Y_1 ~ Z_1)
fit_2 <- lm(Y_2 ~ Z_2)

stargazer(fit_1, fit_2,
          se = makerobustseslist(fit_1, fit_2),
          p = makerobustpslist(fit_1, fit_2), type = "html")
```

